---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%",
  dpi = 300
)
```
# lisa

<!-- badges: start -->
<!-- badges: end -->

This is a color palette R package that contains 128 palettes from [**colorlisa**](http://colorlisa.com/). 

## Installation

You can install `lisa` from GitHub with `devtools`:

``` r
devtools::install_github("tylurp/lisa")
```

## Palettes

Here's a sample of the available palettes:

```{r, include=FALSE}
set.seed(4378)
```


```{r example1, results='hide'}
library(lisa)

par(mfrow = c(6, 3))
lapply(sample(lisa, 18), plot)
```

You can also call and/or modify palettes using `lisa_palette`:

```{r example2, fig.height=1}
x <- lisa_palette("JackBush_1", n = 100, "continuous")
plot(x)
```

## Acknowledgements

* [**colorlisa**](http://colorlisa.com/) for the color palettes
* The [`wesanderson`](https://github.com/karthik/wesanderson) package for source code that powers pretty much everything in this repository.
